%*******************************************************
% Abstract
%*******************************************************
%\renewcommand{\abstractname}{Abstract}
\pdfbookmark[1]{Abstract}{Abstract}
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Abstract}
This master thesis handles the developed of a backend for the smartphone application \glqq History in Paderborn\grqq, using an agile development approach. Furthermore, we will show a draft of the smartphone application. This backend allows students to create content and release their home- and study-work for presentation within a smartphone app, after it has been corrected by the supervisor. The complete workflow is supported by the backend.

Besides the actual development of the application, which is based on Play 2.0 and AngularJS, a part of the topic of this thesis is the methodology within an agile approach itself.

\vfill

\pdfbookmark[1]{Zusammenfassung}{Zusammenfassung}
\chapter*{Zusammenfassung}
Die Masterarbeit behandelt die Umsetzung eines Backends f{\"u}r die Anwendung \glqq History in Paderborn\grqq mit einem agilen Entwicklungsansatz und die Erstellung eines Konzeptes f{\"u}r die dazu passende Smartphone Anwendung. Das Backend der Webanwendung erm{\"o}glicht es Studierenden ihre Haus- und Studienarbeiten zu erstellen und danach f{\"u}r die Anzeige in einer Smartphone app durch einen Betreuer freigeben zu lassen, nachdem diese korrigiert worden sind.  Der komplette Workflow wird hierbei von dem Backend unterst{\"u}tzt.Neben der eigentlichen Entwicklung der Anwendung, die auf dem Play 2.0 Framework und AngularJS basiert, behandelt ein Teil der Arbeit das methodische Vorgehen in einem agilen Ansatz selbst.
\endgroup			

\vfill